%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
\vspace{-3.0mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cyber Security Intern} % Job title
    {Colorado State University} % Organization
    {Fort Collins, CO} % Location
    {Aug. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzing potential threat vectors on the network using Nessus to close potential points of entry}
        \item {Developing a Python module and script to automate Nessus report distribution using the Microsoft Graph API}
        \item {Participated in Capture the Flag events focusing on cryptography, stenography, and packet sniffing}
        \item {Created secure testing environments allowing for group organization and collaboration}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator \& Treasurer} % Job title
    {KryptSec} % Organization
    {Fort Collins, CO} % Location
    {May 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administrator of KryptSec’s knowledge center and it’s SSL certificates}
        \item {Member of a small exclusive group that performed a network examination and penetration test on students enrolled inDr. Stephen Hayne’s course: Advanced Networking and Security}
        \item {Successfully gained footholds via SQL injection, read/write on SMB shares and access a login prompt for RDP}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Technician} % Job title
    {Colorado State University} % Organization
    {Fort Collins, CO} % Location
    {Mar. 2018 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coached over 100 staff members on the use of their hardware and 50+ various software}
        \item {Rapidly transitioned role to training and supporting the CSU community during the COVID-19 Work-From-Home order}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator Intern} % Job title
    {FirstBank Holding Company} % Organization
    {Lakewood, CO} % Location
    {Jun. 2018 - Aug. 2018 \& Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated deployment of virtual machines resulting in 98\% reduction in time using Ansible}
        \item {Developed PowerShell modules to automate the retrieval of the Window’s Registry entries}
        \item {Improved the disaster recovery faculty by deploying over 200 workstations}
        \item {Decreased unscheduled downtime with automated email, text message, and dashboard alerts}
      \end{cvitems}
    }
    

%---------------------------------------------------------
\end{cventries}
